Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-05-02 concurrency/CONCUR 2023/paper.tex
add findnext code

%\wm{Should we recap the definition of the \lstinline{node} struct here?} 
The contents of a BST node are defined in C as:
\begin{lstlisting}[language = C, backgroundcolor=\color{white}, basicstyle=\ttfamily\footnotesize]
	typedef struct node {int key; void *value; struct node_t *left, *right;} node;
\end{lstlisting}
The BST's \lstinline{findNext} function indicates whether the target key is in the current node, its left subtree, or its right subtree. The precondition of \texttt{findNext} (Figure \ref*{fig:findNext_lock}) states that the input has a non-null \texttt{t} field pointing to a \texttt{node} struct with key \texttt{k'}, value \texttt{v'}, and pointers to the left \texttt{l} and right \texttt{r} child nodes. The postcondition describes three possible outcomes: either the provided key \texttt{k} is less than the node's key \texttt{k'}, and the next node \lstinline{n'} is the left child \lstinline{l}; \lstinline{k} is greater than \lstinline{k'} and \lstinline{n'} is the right child \lstinline{r}; or \lstinline{k} is exactly \lstinline{k'} and \lstinline{n'} is the original node \lstinline{n}, in which case the return value is 0. The proof is straightforward. \wm{We should show the actual code for \lstinline{findNext} here!}

>>>>

%\wm{Should we recap the definition of the \lstinline{node} struct here?} 
The contents of a BST node are defined in C as:
\begin{lstlisting}[language = C, backgroundcolor=\color{white}, basicstyle=\ttfamily\footnotesize]
	typedef struct node {int key; void *value; struct node_t *left, *right;} node;
\end{lstlisting}
The BST's \lstinline{findNext} function (Figure \ref{findnext}) indicates whether the target key is in the current node, its left subtree, or its right subtree. The precondition of \texttt{findNext} (Figure \ref*{fig:findNext_lock}) states that the input has a non-null \texttt{t} field pointing to a \texttt{node} struct with key \texttt{k'}, value \texttt{v'}, and pointers to the left \texttt{l} and right \texttt{r} child nodes. The postcondition describes three possible outcomes: either the provided key \texttt{k} is less than the node's key \texttt{k'}, and the next node \lstinline{n'} is the left child \lstinline{l}; \lstinline{k} is greater than \lstinline{k'} and \lstinline{n'} is the right child \lstinline{r}; or \lstinline{k} is exactly \lstinline{k'} and \lstinline{n'} is the original node \lstinline{n}, in which case the return value is 0. The proof is straightforward. %\wm{We should show the actual code for \lstinline{findNext} here!}

\begin{figure}[ht]
	\lstinputlisting[language=C, style=myStyle]{findnext.c} 
	\caption{The \lstinline{findNext} method for binary search tree (all templates) written in C}
	\label{findnext}
\end{figure}
